---
title: "Customizing Plots (solutions)"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(geoscidata)
```

```{r}
warwick
```

## Exercise 1

Modify the following code to use one of ggplot2's built-in themes. Experiment! See `?theme_bw` for a list of themes that can be used.

```{r}
ggplot(warwick) + 
  geom_point(aes(x = Fe_ppm, y = Mn_ppm, color = rock_type))
```

## Exercise 2

Modify the following code to use `scale_color_brewer()`. Experiment with the `palette` argument (see the "Palettes" section of the help file `?scale_color_brewer`) to change the colors (Hint: try `"Spectral"`).

```{r}
ggplot(warwick) + 
  geom_point(aes(x = Fe_ppm, y = Mn_ppm, color = rock_type))
```

## Exercise 3

Create a scatterplot of `warwick` using the `K_ppm` and `Rb_ppm` variables, colored by `rock_type`. Apply your favourite built-in theme, and your favorite color scale using `scale_color_brewer()`.

```{r}

```

***

# Take aways

- Plots can be customized by adding elements using the `+` operator.
- Themes control the non-data appearance of visual elements. The default theme can be replaced by adding a `theme_*()` object to a plot.
- Color scales change the colors that are used to represent data. The default color scale can be replaced by adding `scale_color_brewer()` to a plot.

# More Practice

- The [Exploratory Data Analysis](https://r4ds.had.co.nz/exploratory-data-analysis.html) and [Graphics for Communication](https://r4ds.had.co.nz/graphics-for-communication.html) chapters in [R for Data Science](https://r4ds.had.co.nz/).
- The [Exploratory Data Analysis Primer](https://rstudio.cloud/learn/primers/3.1) and the [Plot Customization Primer](https://rstudio.cloud/learn/primers/3.8) from [RStudio Cloud](https://rstudio.cloud/)
